\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-01-13 paper.tex
Update paper

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, boxrule=0pt, sharp corners, interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi

@@

Expanding upon the information regarding hexagonal binning discussed in
Step 1 of Section~\ref{sec-construct2d}, the primary objective in this
step is to determine the 2D embedding points associated with each
hexagon. As the initial process of hexagonal binning, the 2D points are
clustered into their respective hexagonal bins. By mapping this
information with the hexagonal bin centroids
(\(C_k^{(2)} \equiv (C_{ky_1}, C_{ky_2})\)) that obtained in Step 2 of
the 2D model building (see Section~\ref{sec-construct2d}), we can find
which 2D points are assigned to which data set. (see
Figure~\ref{fig-wkhighD} (a)).

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, breakable, boxrule=0pt, interior hidden, enhanced, frame hidden]}{\end{tcolorbox}}\fi

@@

Expanding upon the information regarding hexagonal binning discussed in
Step 1 of Section~\ref{sec-construct2d}, the primary objective in this
step is to determine the 2D embedding points associated with each
hexagon. As the initial process of hexagonal binning, the 2D points are
clustered into their respective hexagonal bins. By mapping this
information with the hexagonal bin centroids
(\(C_k^{(2)} \equiv (C_{ky_1}, C_{ky_2})\)) that obtained in Step 2 of
the 2D model building (see Section~\ref{sec-construct2d}), we can find
which 2D points are assigned to which data set (see
Figure~\ref{fig-wkhighD} (a)).
